---
title: "Assignment 4 - Coordinating Heart Rate"
author: "Riccardo Fusaroli"
date: "November 6, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Analysing Heart Rate and Respiration data

The goal of this assignment is to first familiarize you with heart rate, and respiration data and their preprocessing. The second part explores how to analyze interpersonal coordination of these signals.

These are the questions you need to be able to answer at the end of the assignment (aka that you need to submit as part of the portfolio)

```{r}
library(ggplot2)
library(crqa)
library(modelr)
library(dplyr)
library(groupdata2)
library(stringr)

#Load data
file_list = list.files('data', pattern = "*.csv", full.names = TRUE)
#data = do.call(rbind, lapply(file_list, read.delim))
#for (i in 1:length(file_list)) assign(file_list[i], read.csv(file_list[i]))

#load single file
test_file = read.csv('data/Study1_G1_T1_Synchronous.csv')
```


1) How do you preprocess heart rate and respiration data? Describe the process. If any data needs to be excluded, list the excluded data and motivate the exclusion.

```{r}
#------ Preprocessing for test file ------

#Artifacts
#Define function for removing outliers
removeOuts = function(ts,threshold){
  ts[ts > (mean(ts,na.rm=T) + (threshold*sd(ts,na.rm=T))) | ts < (mean(ts,na.rm=T) - (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)
  return(ts)}

#Set threshhold
threshold=2.5 

#remove outliers
test_file$HR1=removeOuts(test_file$HR1,threshold)

ggplot(test_file, aes(time, HR1))+geom_point()
ggplot(test_file, aes(HR1))+ geom_histogram()

#Downsample
test_file = test_file %>% group(n= 100, method= 'greedy') %>% dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T), HR2 = mean(HR2,na.rm=T), Resp1 = mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T))

#Scale
test_file$HR1 = scale(test_file$HR1)
test_file$HR2 = scale(test_file$HR2)
test_file$Resp1 = scale(test_file$Resp1)
test_file$Resp2 = scale(test_file$Resp2)

```


```{r}
#Preprocessing function
Prepro = function(path){

  #read
  file = read.csv(path)
  
  #------ Remove outliers ------
  removeOuts = function(ts,threshold){
   ts[ts > (mean(ts,na.rm=T) + (threshold*sd(ts,na.rm=T))) | ts < (mean(ts,na.rm=T) - (threshold*sd(ts,na.rm=T)))] = mean(ts,na.rm=T)
  return(ts)}

  #Set threshhold
  threshold=2.5 

  #remove outliers
  file$HR1=removeOuts(file$HR1,threshold)
  file$HR2=removeOuts(file$HR2,threshold)
  file$Resp1=removeOuts(file$Resp1,threshold)
  file$Resp2=removeOuts(file$Resp2,threshold)


  #------ Downsample ------
  file = file %>% group(n= 100, method= 'greedy') %>% dplyr::summarise(time = mean(time,na.rm=T), HR1 = mean(HR1,na.rm=T), HR2 = mean(HR2,na.rm=T), Resp1 = mean(Resp1,na.rm=T), Resp2 = mean(Resp2,na.rm=T))

  #------ Scale ------
  file$HR1 = scale(file$HR1)
  file$HR2 = scale(file$HR2)
  file$Resp1 = scale(file$Resp1)
  file$Resp2 = scale(file$Resp2)
  
  #Write file
  filename = paste("PP_data/PP_", substring(path, first = 6, last = 1000000))
  file = write.csv(file, file = filename)
  
  return(file)
}

#Use preprocessing on list
#lapply(file_list, Prepro)

# Making filelist of preprocessed data files
pp_file_list = list.files('PP_data', pattern = "*.csv", full.names = TRUE)


#Test line for loop below
#ggplot(test_file, aes(time, HR1))+geom_line()+labs(title = "hallo")

# ggplot loop to see if there are still artifacts in pp data
for (file in pp_file_list) {
  dest = paste("", file, sep = '')
  #Read file
  x = read.csv(dest, header = TRUE)
  
  #filename = paste(substring(file, first = 12, last = 1000000))
  
  print(ggplot(x, aes(time, HR1))+geom_line()+labs(title = file))
 # ggsave()
  print(ggplot(x, aes(time, HR2))+geom_line()+labs(title = file))
  print(ggplot(x, aes(time, Resp1))+geom_line()+labs(title = file))
  print(ggplot(x, aes(time, Resp2))+geom_line()+labs(title = file))
}

#Manually removed files where the plots showed artifacts from the folder.


```

2) Do you observe interpersonal coordination in heart rate and respiration? Describe your control baseline, the method used to quantify coordination, and the statistical models used to infer whether coordination was higher than in the baseline. Report the results of the models.

#Loop 1 med data fra filnavn, descriptive stats, optimale parametre
#Loop 2 Kør CRQA med median parameter
#Step 3 profit


```{r}
#Make list of files to run through
PP_final = list.files('PP_data', pattern = "*.csv", full.names = TRUE)

#standard parameters
par = list(lgM =  15, steps = seq(1, 6, 1),  radiusspan = 100,  radiussample = 15, normalize = 0,  rescale = 0,  mindiagline = 2,  minvertline = 2,  tw = 0,  whiteline = FALSE,  recpt = FALSE,  fnnpercent = 10,  typeami = "mindip")

#null list
loop1DF = data.frame()

#i = PP_final[1]

#Loop1: preprocessing and optimizing parameters
for (i in PP_final){
  #------ Read file ------
  file = read.csv(i, header = TRUE)
  
  #------ Extract info from filename ------
  extract = str_extract_all(i, "\\d+", simplify = TRUE)
  Study = extract[1]
  Pair_number = extract[2]
  Condition = extract[3]
  
  
  #------ Find optimal parameters ------
  #If parameters are found: save them. Else: save as NA
  #heart rate
  ans_heart = try(optimizeParam(file$HR1, file$HR2, par, min.rec = 3, max.rec = 5))
     if (length(ans_heart) > 1) {
       radius_h = ans_heart$radius
       emddim_h = ans_heart$emddim
       delay_h = ans_heart$delay
     } else {
       radius_h = NA
       emddim_h = NA
       delay_h = NA
     }
  
  #  Respiration rate
  ans_resp = try(optimizeParam(file$Resp1, file$Resp2, par, min.rec = 3, max.rec = 5))
     if (length(ans_resp) > 1) {
       radius_r = ans_resp$radius
       emddim_r = ans_resp$emddim
       delay_r = ans_resp$delay
     } else {
       radius_r = NA
       emddim_r = NA
       delay_r = NA
     }
  
  #------ Save data ------
  #Make relevant information into a one row data frame
  df_result = data.frame(Study, 
                             Pair_number, 
                             Condition, 
                             radius_h, 
                             emddim_h, 
                             delay_h,
                             radius_r, 
                             emddim_r, 
                             delay_r
                             )
  #Bind the above row to the actual dataset for loop 1
  loop1DF = rbind(loop1DF, df_result)
  }


#------ Median parameters for loop 2 ------
median_radius_h = median(loop1DF$radius_h, na.rm = TRUE)
median_emddim_h = median(loop1DF$emddim_h, na.rm = TRUE)
median_delay_h = median(loop1DF$delay_h, na.rm = TRUE)

median_radius_r = median(loop1DF$radius_r, na.rm = TRUE)
median_emddim_r = median(loop1DF$emddim_r, na.rm = TRUE)
median_delay_r = median(loop1DF$delay_r, na.rm = TRUE)

#------ Null list for loop 2 ------
loop2DF = data.frame()

i = PP_final[1]

crqa_func = function(file){
#------ Loop 2: CRQA ------
#for (i in PP_final){
  #------ Read file ------
  file = read.csv(i, header = TRUE)
  
  #------ Extract info from filename ------
  extract = str_extract_all(i, "\\d+", simplify = TRUE)
  Study = extract[1]
  Pair_number = extract[2]
  Condition = extract[3]
  
  #------ CRQA ------
  #Heart rate
  a_h = try(crqa(file$HR1, file$HR2,delay = median_delay_h, embed= median_emddim_h, radius= median_radius_h,normalize=0,rescale=0,mindiagline = 2,minvertline = 2))
  
  #If analysis fails, record NA
  if (length(a_h) > 2) {
    RR_h = a_h[1]
    DET_h = a_h[2]
    NRLINE_h = a_h[3]
    maxL_h = a_h[4]
    L_h = a_h[5]
    ENTR_h = a_h[6]
    rENTR_h = a_h[7]
    LAM_h = a_h[8]
    TT_h = a_h[9]
  }
  else {
    RR_h = NA
    DET_h = NA
    NRLINE_h = NA
    maxL_h = NA
    L_h = NA
    ENTR_h = NA
    rENTR_h = NA
    LAM_h = NA
    TT_h = NA
  }
  #Respiration rate
  a_r = try(crqa(file$Resp1, file$Resp2,delay = median_delay_r, embed= median_emddim_r, radius= median_radius_r,normalize=0,rescale=0,mindiagline = 2,minvertline = 2))
  
  #If analysis fails, record NA
  if (length(a_h) > 2) {
    RR_r = a_r[1]
    DET_r = a_r[2]
    NRLINE_r = a_r[3]
    maxL_r = a_r[4]
    L_r = a_r[5]
    ENTR_r = a_r[6]
    rENTR_r = a_r[7]
    LAM_r = a_r[8]
    TT_r = a_r[9]
  }
  else {
    RR_r = NA
    DET_r = NA
    NRLINE_r = NA
    maxL_r = NA
    L_r = NA
    ENTR_r = NA
    rENTR_r = NA
    LAM_r = NA
    TT_r = NA
  }
  

  #------ Make dataframe ------  
  #Make relevant information into a one row data frame
  df_result = data.frame(Study, 
                             Pair_number, 
                             Condition, 
    RR_h, DET_h, NRLINE_h, maxL_h, L_h, ENTR_h, rENTR_h, LAM_h, TT_h, 
    RR_r, DET_r, NRLINE_r, maxL_r, L_r, ENTR_r, rENTR_r, LAM_r, TT_r
                             )
  
  #Bind the above row to the actual dataset for loop 2
  loop2DF = rbind(loop2DF, df_result)
  
  return(loop2DF)
}


 dflist = list()
 n = 1

# loop for files
for (i in PP_final){
  file = read.csv(i, header = TRUE)
  
  #  #------ Extract info from filename ------
  # extract = str_extract_all(i, "\\d+", simplify = TRUE)
  # Study = extract[1]
  # Pair_number = extract[2]
  # Condition = extract[3]
 
  dflist[n] = file
  n + 1
}


lapply(crqa_func, PP_final)

loop2DF_shuf = data.frame()

# SHUFFLING SHIT UP

for (i in PP_final) {
  file = read.csv(i, header = TRUE)
  
  extract = str_extract_all(i, "\\d+", simplify = TRUE)
  Study = extract[1]
  Pair_number = extract[2]
  Condition = extract[3]
  
  s_HR1 = sample(file$HR1)
  s_HR2 = sample(file$HR2)
  s_Resp1 = sample(file$Resp1)
  s_Resp2 = sample(file$Resp2)
  
  #------ CRQA ------
  #Heart rate
  a_h = try(crqa(s_HR1, s_HR2,delay = median_delay_h, embed= median_emddim_h, radius= median_radius_h,normalize=0,rescale=0,mindiagline = 2,minvertline = 2))
  
  #If analysis fails, record NA
  if (length(a_h) > 2) {
    RR_h = a_h[1]
    DET_h = a_h[2]
    NRLINE_h = a_h[3]
    maxL_h = a_h[4]
    L_h = a_h[5]
    ENTR_h = a_h[6]
    rENTR_h = a_h[7]
    LAM_h = a_h[8]
    TT_h = a_h[9]
  }
  else {
    RR_h = NA
    DET_h = NA
    NRLINE_h = NA
    maxL_h = NA
    L_h = NA
    ENTR_h = NA
    rENTR_h = NA
    LAM_h = NA
    TT_h = NA
  }
  #Respiration rate
  a_r = try(crqa(s_Resp1, s_Resp2,delay = median_delay_r, embed= median_emddim_r, radius= median_radius_r,normalize=0,rescale=0,mindiagline = 2,minvertline = 2))
  
  #If analysis fails, record NA
  if (length(a_h) > 2) {
    RR_r = a_r[1]
    DET_r = a_r[2]
    NRLINE_r = a_r[3]
    maxL_r = a_r[4]
    L_r = a_r[5]
    ENTR_r = a_r[6]
    rENTR_r = a_r[7]
    LAM_r = a_r[8]
    TT_r = a_r[9]
  }
  else {
    RR_r = NA
    DET_r = NA
    NRLINE_r = NA
    maxL_r = NA
    L_r = NA
    ENTR_r = NA
    rENTR_r = NA
    LAM_r = NA
    TT_r = NA
  }
  

  #------ Make dataframe ------  
  #Make relevant information into a one row data frame
  df_result = data.frame(Study, 
                             Pair_number, 
                             Condition, 
    RR_h, DET_h, NRLINE_h, maxL_h, L_h, ENTR_h, rENTR_h, LAM_h, TT_h, 
    RR_r, DET_r, NRLINE_r, maxL_r, L_r, ENTR_r, rENTR_r, LAM_r, TT_r
                             )
  
  #Bind the above row to the actual dataset for loop 2
  loop2DF_shuf = rbind(loop2DF_shuf, df_result)
  
}


# SUROGATE PAIRS




# MODELS

m_int = lmer()


```


3) Do you observe differences in coordination between conditions? Report the models and results.

```{r}

```


4) Is respiration coordination a likely driver of heart rate coordination? Describe how you would test for it. Bonus points if you actually run the tests and report methods and results.

N.B. to give you a bit more data I included data from last year (Study1) and from your class (Study2). Note that synchronouns and turn-taking are the same across both studies, but the third condition is different: last year it was self-paced joint reading; this year it was the tv-series conversation. So you might want to exclude the self-paced reading (but, up to you!)

## Step by step suggestions to solve the assignment

### Exploring physiological signals

- Choose one pair (one pair, three conditions)
- Load the logs
- Produce a plot of the participants' respiration signal and a different one of the participants' HR signal (for inspecting whether the data is usable)
  N.B: remember the slides: artifacts, downsampling, scaling.
  N.B. The gridExtra::grid.arrange() function allows you to display the plots side by side. E.g. grid.arrange(plot1, plot2, plot3, ncol=3)
- Can you eye-ball which condition if any displays more physiological coordination?

- Run crqa on heart rate and respiration data (find parameters, run crqa)
- Does this tell you more than just eyeballing the plots?

### Systematically pre-process the data
- Loop through all the files (either with a loop or with a function), check which files should be excluded, if any, and save the pre-processed time-series. Tip: plot and visually inspect the data to figure out which should be excluded.
- Run crqa on all the pre-processed time-series and save the output (don't forget to add columns with study, group, condition and trial). Tip: remember to first assess optimal parameters (dimensions, delay, radius) across all timeseries. Tip: it will often fail, just take whatever parameters you get, select optimal across timeseries parameters and run crqa on all timeseries with those. Tip: double check the rr. When I ran the loop, I got very low rr, so I adjusted the radius until the average of rr across all pairs was approx. 4%.

### Creating controls: shuffled controls
 - loop through all pairs and conditions
 - shuffle the timeseries (take a timeseries and rearrange its values in a random order). Tip check the sample() function
 - run crqa and save the output. NB. which delay, embed, radius parameters should you use?
 - statistically compare the crqa indexes in real and shuffled pairs
 
### TRICKY! Creating controls: surrogate pair controls
 - Per each real pair, identify at least one surrogate pair (matching one of the participants, with somebody doing the same task, but in a different pair). Tip: Celine will share a commented script
 - Run crqa on all the surrogate pairs and save the output. NB. which delay, embed, radius parameters should you use?
 - Test whether crqa shows a difference between real and surrogate pairs

### Testing effects of conditions
 - make a (probably underpowered) mixed model testing effects of the different conditions on heart rate and respiration coordination
 - N.B: would it make sense to include surrogate pairs? and if so how? what would that tell you?

### Effects of respiration coordination on heart rate coordination
 - describe how you would test those.
 - Optional: run the models and report them